Short-term neuronal and synaptic plasticity act in synergy for deviance detection in spiking networks

### 2023-01-12 paper-1/manuscript.tex
Edit F7 layout (early/late horizontal like in F6)

\begin{figure*}%
    \centering
    \includegraphics{fig7.pdf}
    \caption{}
    \label{fig7}
\end{figure*}
\textbf{Fig. 7} Adding STD to the model maintains or slighly enhances the effects of TA.
\textbf{a} Median contrast (\dev{} - \msc{}) in the non-target response (left) and in $\theta$ at the start of B trials (right) among early and late neurons, respectively, across networks and stimuli, in the full model with both STD and TA. Compare to Figure \ref{fig6}c-d.
\textbf{b} Median contrast (\dev{} - \msc{}) in the non-target response magnitude across networks and stimuli in the full model (horizontal axis) and the ablated model with TA only (vertical axis). The red line is the identity function; points above this line represent networks with greater response reduction (\dev{} - \msc{}) in the full model than in the ablated model. The subtraction of the two quantities in the box plot below shows that the non-target response tends to be reduced more in the full model.
\textbf{c} Non-target response contrast, plotted against its Pearson correlation coefficient with the corresponding contrast in $\theta$ at the start of target trials, in the full model. Compare to Figure \ref{fig5}d.
\textbf{d} Median contrast (\dev{} - \msc{}) in $\theta$ at the start of target trials across networks and stimuli in the full and ablated models, arranged as in panel b. The subtraction of the two quantities in the box plot below shows that $\theta$ tends to be reduced more in the full model.
\textbf{e} $\Delta \theta$ at the start of target trials, plotted against its Pearson correlation coefficient with the corresponding contrast in the target response magnitude, in the full model. Compare to Figure \ref{fig4}e.
\textbf{f} Median contrast (\dev{} - \msc{}) in the target response magnitude across networks and stimuli in the full and ablated models, arranged as in panel b. The subtraction of the two quantities in the box plot below shows that the target response tends to be increased more in the full model

>>>>

\begin{figure*}%
    \centering
    \includegraphics{fig7.pdf}
    \caption{}
    \label{fig7}
\end{figure*}
\textbf{Fig. 7} Adding STD to the model maintains or slighly enhances the effects of TA.
\textbf{a} Median contrast (\dev{} - \msc{}) in the non-target response (top) and in $\theta$ at the start of B trials (bottom) among early and late neurons, respectively, across networks and stimuli, in the full model with both STD and TA. Compare to Figure \ref{fig6}c-d.
\textbf{b} Median contrast (\dev{} - \msc{}) in the non-target response magnitude across networks and stimuli in the full model (horizontal axis) and the ablated model with TA only (vertical axis). The red line is the identity function; points above this line represent networks with greater response reduction (\dev{} - \msc{}) in the full model than in the ablated model. The subtraction of the two quantities in the box plot below shows that the non-target response tends to be reduced more in the full model.
\textbf{c} Non-target response contrast, plotted against its Pearson correlation coefficient with the corresponding contrast in $\theta$ at the start of target trials, in the full model. Compare to Figure \ref{fig5}d.
\textbf{d} Median contrast (\dev{} - \msc{}) in $\theta$ at the start of target trials across networks and stimuli in the full and ablated models, arranged as in panel b. The subtraction of the two quantities in the box plot below shows that $\theta$ tends to be reduced more in the full model.
\textbf{e} $\Delta \theta$ at the start of target trials, plotted against its Pearson correlation coefficient with the corresponding contrast in the target response magnitude, in the full model. Compare to Figure \ref{fig4}e.
\textbf{f} Median contrast (\dev{} - \msc{}) in the target response magnitude across networks and stimuli in the full and ablated models, arranged as in panel b. The subtraction of the two quantities in the box plot below shows that the target response tends to be increased more in the full model
